---
title: "individual1"
output: html_document
---
```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```

## 1. Question Set

1. The chocolate ratings have a Normal distribution. There are two outliers with a score of 5.
```{r}
hist(choco$Rating, xlab = "Rating", main = "Distribution of Chocolate Ratings")
```

```{r}
which.max(choco$Rating)
#Finding maximum score
choco[87, 'Rating']
#Location of maximum score
choco[choco$Rating == '5',]
#Searching for multiples of maximum score
```


2. No, the ratings are not significantly affected by the cacao percentage. They are very slightly negatively correlated, with an inconclusive barplot.

```{r}
barplot(choco$Cocoa.Pct, choco$Rating)

cor(choco$Cocoa.Pct, choco$Rating)
```


3. Company.Location is a factor, which is a data structure similar to a dataframe, and can be ordered or unordered but represent categorical data. Characters represent string values in R, while factors are stored as integers although they look like characters to us. 

```{r}
typeof(choco$Company.Location)
```



